---
title: "Basic Usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basic Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(glossaries)
```

```{r}
load_entries(system.file('example/myglossary.yml',package = 'glossaries'))
```

```{r}
add_definition(
  entry = 'turtle',
  name = 'turtle',
  desc = 'a large marine reptile with a bony or leathery shell and flippers, coming ashore annually on sandy beaches to lay egg'
  )
```

```{r}
add_acronym(
  entry = 'aic',
  label = 'AIC',
  long = 'akaike information criterion'
)

add_acronym(
  entry = 'bic',
  label = 'BIC',
  long = 'bayes information criterion'
)
```

## Definitions

```{r, echo=FALSE}
get_entries('definition')%>%
  glossary_to_table()%>%
  knitr::kable(col.names = c('Term',''))
```

## Acronyms

```{r, echo=FALSE}
get_entries('acronym')%>%
  glossary_to_table()%>%
  knitr::kable(col.names = c('Term',''))
```

## Examples

### Information Criteria

In statistics, the `r Gls('bic')` or Schwarz information criterion (also SIC, SBC, SBIC) is a criterion for model selection among a finite set of models; the model with the lowest `r gls('bic')` is preferred. It is based, in part, on the likelihood function and it is closely related to the `r Gls('aic')`.

When fitting models, it is possible to increase the likelihood by adding parameters, but doing so may result in overfitting. Both `r gls('bic')` and `r gls('aic')` attempt to resolve this problem by introducing a penalty term for the number of parameters in the model; the penalty term is larger in `r gls('bic')` than in `r gls('aic')`

The `r gls('bic')` was developed by Gideon E. Schwarz and published in a 1978 paper, where he gave a Bayesian argument for adopting it.

### `r Glspl('turtle')`

The `r gls('po')` is the largest and deepest of Earth's oceanic divisions. It extends from the Arctic `r Gls('ocean')` in the north to the Southern `r Gls('ocean')` (or, depending on definition, to Antarctica) in the south and is bounded by the continents of Asia and Australia in the west and the Americas in the east.

Sea `r gls('turtle')` live in the Nothern `r gls('po')` one or more life stages, from hatchling to adult. This includes green, loggerhead, olive ridley, leatherback, and hawksbill sea `r glspl('turtle')`—all of which are protected under the U.S. Endangered Species Act.

